
\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Darshan N}} & Email: \href{mailto:}{darshan51081@gmail.com}\\
  \href{https://www.linkedin.com/in/darshn-n/}{LinkedIn: Darshan N} & Mobile:~~~+91 7483442068 \\
  \href{https://github.com/darshn-n}{Github: ~~darshn-n} \\
  {Location: Mysuru, Karnataka}
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {JSS Science and Technology University
}{Mysuru, India}
      {B.E in Electronics and Communication Engineering
;  GPA: 8.4}{December 2020 - June 2024}
\resumeSubheading
      {Maharaja Government PU College}{Mysuru, India}
      {PUC
;  Percentage: 89.6}{June 2018 - June 2020}
\resumeSubheading
      {JSS High School}{Mysuru, India}
      {SSLC
;  Percentage: 96.6}{June 2015 - April 2018}
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C++, Python, Dart, C, JavaScript}
	\resumeSubItem{Frameworks}{~~~~Flutter, Bootstrap, jQuery, SciPy}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, MySQL, Slack, Visual Studio, IDEs}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Windows, Firebase}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}
\vspace{8pt}
\resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Prodigal AI Intern}{Remote}
    {Flutter Developer}{Nov 2022}
    \resumeItemListStart
    \resumeItem{Developed a Cross Platform Application}
          {for both Google PlayStore and AppStore using Flutter SDK and Node.js backend.}
          \resumeItem{Google Maps APIs and Access Permissions}
          {Accessing user's current location to show the required data.}
          \resumeItem{Node JS backend with Flutter SDK}{Implemented a backend for real time updates and Application UI updates.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Awards-----------------
\section{Areas of Interest}
\begin{description}[font=$\bullet$]
\vspace{5pt}
\item {Cross Platform App Development}
\vspace{-5pt}
\item {Web Development}
\vspace{-5pt}
\item {Competitive Programming}

\end{description}



%-----------PROJECTS-----------------
\vspace{5pt}
\section{Projects}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubItem{Opportunes - A New Job Finding App(Job Finder based different Categories with User and Admin Access.)}{Cloud based Data Upload, User End and Admin end seperate Apps, CRUD using Firebase, Google Authentication using Firebase, Help Center for Resume Instructions and Career Guidance. Tech: Dart, Google Cloud, Firebase, Shared Preferences.(May '22)}
\vspace{2pt}
\resumeSubItem{Regime - Daily Routine Tracker(A Routine maintaining app with Local Phone Storage.)}{User's Local Database, Daily Routine Streaks implementation, CRUD Operations using Local Database. Tech: Dart, Hive-Local Database, Provider (May '22)}
\vspace{2pt}
\resumeSubItem{VentureX Web Application (JSSSTU's very own E-Cell Web Application.)}{Compatible for All Devices, Backend Idea Portal Support, First Web App with Bottom Nav Bar feature. Tech: Flutter HTML, CSS, JS, BootStrap (Nov '22)}
\vspace{2pt}
\resumeSubItem{Temperature Controlled Fan using 8051 Microcontroller(Hardware and Software Implementation using Proteus)}{A microcontroller is used to control the speed of the fan according to the temperature and specify the temperature in the display. Tech: Embedded C, Proteus(August '22)}
\vspace{2pt}
\resumeSubItem{EV Buddy(Displays EV charging location using user's current location.)}{Fetching user's current location, Phone Auth using Node.js, Provider and Shared preferences for State management. Tech: Flutter, Node.js, Google Cloud( May '12)}
\resumeSubHeadingListEnd
\vspace{5pt}

% Pubs

\section{Publications}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubItem{Pub.dev Package: Network Image Search(Flutter Development)}{A new Flutter Package which helps to search Unsplash Network Images from multiple websites with customizable width and height. Compatible to Android and iOS.
}
\vspace{2pt}
\resumeSubItem{Pub.dev Package: Flutter FAB Visibility(Flutter Development)}{A new Flutter package that hides the Floating action button when Up Scrolled, and visible when Down Scrolled.}
\resumeSubHeadingListEnd

\vspace{5pt}
\section{Responsibilities}
\vspace{5pt}

  \resumeSubHeadingListStart
	\resumeSubheading
    {Web Developer at VentureX SJCE}{Mysuru, India}
    {Conducted online and offline technical \& soft-skills events.}{July 2022 - Present}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Technical Co-ordinator at K-Tech SJCE }{Mysuru, India}
    {Powered by Nain-SJCE}{August 2021 - Present}

\resumeSubHeadingListEnd

\end{document}
