
\documentclass[]{rahulworld-resume}


\begin{document}


\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Darshan N}\\
\end{large}
III Year (B.E)\\
ECE\\ 
JSSSTU, Mysuru
 \\ 
CGPA:8.35 till 5th Sem 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}
\noindent\rule{5cm}{0.4pt}
\vspace{6pt}\\
To gain knowledge, experience and to\\
build a career with leading corporate\\
environment. Seeking full time career\\
with an organization, which will permit\\ me
to use and contribute my abilities\\ to
enhance my knowledge by \\committed and
high-quality work.





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2020-2024}
\subsection{B.E. in ECE}
JSS Science and Technology University
 \\
CGPA : 8.7/10(Expected)\\
\vspace{8pt}
\datecolor{2018-2020}
\subsection{PUC}
Maharaja Government PU College\\
Percentage: 89.6\%\\
\vspace{8pt}
\datecolor{2015-2018}
\subsection{High School}
JSS High School , Mysuru\\
Percentage: 96.6\%
\sectionsep



\section{Skills}
\noindent\rule{5cm}{0.4pt}
\vspace{6pt}
\subsection{Languages}
C/C++, Python, Javascript, Dart
\vspace{6pt}
\subsection{OS}
Linux, Windows
\vspace{6pt}
\subsection{Framework}
Flutter, jQuery, \\ Node.js,
Web App development
\vspace{6pt}
\subsection{Databases}
MySQL, Firebase, MongoDB
\vspace{6pt}
\subsection{Soft Skills}
* Leadership and Teamwork
\\
* Time Management\\
* Analytical thinking

\sectionsep



\section{Areas of Interest}
\noindent\rule{5cm}{0.4pt}
\vspace{6pt}\\
* Cross Platform App Development\\
* Web Development.\\
* Competitive Programming.


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\hspace*{0pt}\hfill Mysuru, Karnataka\\
\hspace*{0pt}\hfill Mob.: +91-7483442068 \\
\hspace*{0pt}\hfill Github.:\textbf{\href{https://github.com/darshn-n}{darshn-n}} 

\hspace*{0pt}\hfill 
\hspace*{0pt}\hfill LinkedIn.:\textbf{\href{https://www.linkedin.com/in/darshn-n/}{Darshan N}} 
 

\hspace*{0pt}\hfill 
Email.:\textbf{\href{mailto:darshan51081@gmail.com}{darshan51081@gmail.com}} \\
 \\
% Github:\href{}{\custombold{darshn-n}} \\
% LinkedIn: \href{https://www.linkedin.com/in/darshn-n/}{\custombold{Darshan N}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2021-2022} \runsubsection{Flutter Intern(Remote)}
\descript{Prodigal AI}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
* Developed a Cross Platform Application: for both Google PlayStore and AppStore using Flutter SDK and Node.js
backend.\\
* Google Maps APIs and Access Permissions: Accessing location
\end{minipage}
\descriptright{Tech: Flutter, Node.js, Google Cloud}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects and Publications}
\noindent\rule{12.5cm}{0.4pt}
\runsubsection{\href{https://play.google.com/store/apps/details?id=com.opportunes.opportunes}{Opportunes - A New Job Finding App.}}
\descript{Flutter, Google Cloud, Firebase}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Job Finder based different Categories with User and Admin Access. Cloud based Data Upload, User End and Admin end seperate Apps, CRUD using Firebase. (May 2022)
\end{minipage}
\runsubsection{\href{https://play.google.com/store/apps/details?id=com.darshan.routine}{Regime - Daily Routine Tracke}}
\descript{ Flutter, Hive-Local Database.}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A Routine maintaining app with Local Phone Storage. User's Local Database, Daily Routine Streaks implementation, CRUD Operations using Local Database. (September 2022)
\end{minipage}
\runsubsection{\href{https://venturex.netlify.app/}{VentureX Web Application.}}
\descript{Flutter Web, HTML, CSS, JS, BootStrap}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
JSSSTU's very own E-Cell Web Application. Compatible for All Devices, Backend Idea Portal Support. (Nov 2022)
\end{minipage}
\runsubsection{Temperature Controlled Fan using 8051}
\descript{Embedded C, Proteus}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A microcontroller is used to control the speed of the fan according to the temperature and specify it in the display. (Jan 2022)
\end{minipage}
\runsubsection{EV Buddy - by Prodigal AI}
\descript{Flutter, Node.js, Google Cloud}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Displays EV charging location using user's current location.
Fetching user's current location, Phone Auth using Node.js. (Nov 2022)
\end{minipage}
\runsubsection{\href{https://pub.dev/packages/network_image_search}{Pub.dev Package: Network Image Search}}
\descript{Flutter, APIs}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A new Flutter Package which helps to search Unsplash Network Images from multiple websites with customizable width and height. Compatible to Android and iOS.(Sept 2022)
\end{minipage}




\section{Responsibilities} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2022-now} \runsubsection{Web Developer at VentureX SJCE}

\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Conducted online and offline technical & soft-skills events.\end{minipage}\\\\
\datecolor{2021-now} \runsubsection{Technical Co-ordinator in K-Tech SJCE}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Powered by Nain-SJCE
\end{minipage}

\section{Hobbies}
\noindent\rule{5cm}{0.4pt}
\vspace{6pt}\\
* Stage Performances  \hspace{1em}
* Free Style Dancing  \hspace{1em}
* Elongated Cardios

\sectionsep

\end{minipage} 





\end{document}  \documentclass[]{article}
